\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
rearrange sections
add section on editour server disk throttling

% useful packages
\usepackage[utf8]{inputenc} % UTF-8 support
\usepackage{minted} % for code snippets
\usepackage[american]{babel} % for changing particular titles
\usepackage{csquotes} % recommended for biblatex
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol

\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables
\usepackage{CJKutf8} % for Japanese UTF-8 characters

@@

\subsection{Current Augmented Reality Technology}
\label{sec:currentAugmentedRealityTechnology}

@@

\subsection{Augmented Reality Use Cases}
\label{sec:augmentedRealityUseCases}

@@

\subsection{Challenges of Augmented Reality}
\label{sec:challengesOfAugmentedReality}

@@

\subsection{Apps for Art and Culture}
\label{sec:appsForArtAndCulture}

To explore existing AR apps for art and culture our group researched and tested
several games, experiences, and platforms related to our project.

\subsubsection{izi.TRAVEL}
\label{sec:iziTravel}

@@

\subsection{Platforms}
\label{sec:platforms}

@@

>>>>

% useful packages
\usepackage[utf8]{inputenc} % UTF-8 support
\usepackage{minted} % for code snippets
\usepackage[american]{babel} % for changing particular titles
\usepackage{csquotes} % recommended for biblatex
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol
\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables
\usepackage{CJKutf8} % for Japanese UTF-8 characters

@@

\subsubsection{Current Augmented Reality Technology}
\label{sec:currentAugmentedRealityTechnology}

@@

\subsubsection{Augmented Reality Use Cases}
\label{sec:augmentedRealityUseCases}

@@

\subsubsection{Challenges of Augmented Reality}
\label{sec:challengesOfAugmentedReality}

@@

\subsection{izi.TRAVEL}
\label{sec:iziTravel}

@@

\subsection{Augmented Reality Platforms}
\label{sec:platforms}

@@

Unfortunately, the hosting provider Kyoto VR provided us with severely throttles
disk write speeds. Because the backend has to write potentially large amounts of
data to the disk every time a tour is uploaded or edited this becomes a major
bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
this can cause an issue where the Node server takes so long to respond that
Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
message~\autocite{rfc7231}. Without access to superuser permissions or a faster
hosting provider there is nothing we can do about this bug. The Node server does
eventually complete the request and respond correctly, so until Kyoto VR can get
a better hosting provider we consider it a minor issue.
